Metascatter: Unifying Symbiotic Radio and Intelligent Reflecting Surface

### 2022-06-18 assets/distribution_weight.tex
:bento: Update assets

\begin{axis}[%
width=4.036in,
height=3.396in,
at={(0.677in,0.458in)},
scale only axis,
xmin=1,
xmax=4,
xtick={1, 2, 3, 4},
xlabel style={font=\color{white!15!black}},
xlabel={Reflection State},
ymin=0,
ymax=1,
ylabel style={font=\color{white!15!black}},
ylabel={Probability Distribution},
axis background/.style={fill=white},
xminorgrids,
yminorgrids,
legend style={legend cell align=left, align=left, draw=white!15!black},
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot [color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}]
  table[row sep=crcr]{%
1	0.249999735242584\\
2	0.250000264588401\\
3	0.250000265053761\\
4	0.249999735115254\\
};
\addlegendentry{$\rho =0$}

\addplot [color=mycolor2, dashed, line width=2.0pt, mark=+, mark options={solid, mycolor2}]
  table[row sep=crcr]{%
1	0.295743068427155\\
2	0.375240201334651\\
3	0.156312315031268\\
4	0.172704415206926\\
};
\addlegendentry{$\rho =0.002$}

\addplot [color=mycolor3, dotted, line width=2.0pt, mark=square, mark options={solid, mycolor3}]
  table[row sep=crcr]{%
1	0.261901350518658\\
2	0.712510408293707\\
3	0.00842749500731859\\
4	0.0171607461803161\\
};
\addlegendentry{$\rho =0.005$}

\addplot [color=mycolor4, dashdotted, line width=2.0pt, mark=x, mark options={solid, mycolor4}]
  table[row sep=crcr]{%
1	0.139913707035647\\
2	0.859278410930712\\
3	0.000142053828609263\\
4	0.000665828205031897\\
};
\addlegendentry{$\rho =0.01$}

\addplot [color=mycolor5, line width=2.0pt, mark=triangle, mark options={solid, mycolor5}]
  table[row sep=crcr]{%
1	1.29237706072384e-05\\
2	0.999987076229393\\
3	4.46101240540389e-26\\
4	3.49723978579285e-21\\
};
\addlegendentry{$\rho =1$}

>>>>

\begin{axis}[%
width=4.036in,
height=3.396in,
at={(0.677in,0.458in)},
scale only axis,
xmin=1,
xmax=4,
xtick={1, 2, 3, 4},
xlabel style={font=\color{white!15!black}},
xlabel={Reflection State},
ymin=0,
ymax=1,
ylabel style={font=\color{white!15!black}},
ylabel={Probability Distribution},
axis background/.style={fill=white},
xminorgrids,
yminorgrids,
legend style={legend cell align=left, align=left, draw=white!15!black},
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot [color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}]
  table[row sep=crcr]{%
1	0.249999734945382\\
2	0.250000264528953\\
3	0.25000026543652\\
4	0.249999735089145\\
};
\addlegendentry{$\rho =0$}

\addplot [color=mycolor2, dashed, line width=2.0pt, mark=+, mark options={solid, mycolor2}]
  table[row sep=crcr]{%
1	0.29621586579285\\
2	0.376168737406121\\
3	0.155469818621155\\
4	0.172145578179874\\
};
\addlegendentry{$\rho =0.02$}

\addplot [color=mycolor3, dotted, line width=2.0pt, mark=square, mark options={solid, mycolor3}]
  table[row sep=crcr]{%
1	0.262448276431783\\
2	0.712350409003269\\
3	0.00824022832841558\\
4	0.0169610862365327\\
};
\addlegendentry{$\rho =0.05$}

\addplot [color=mycolor4, dashdotted, line width=2.0pt, mark=x, mark options={solid, mycolor4}]
  table[row sep=crcr]{%
1	0.140066723576523\\
2	0.859156695957714\\
3	0.000133936954753823\\
4	0.000642643511009231\\
};
\addlegendentry{$\rho =0.1$}

\addplot [color=mycolor5, line width=2.0pt, mark=triangle, mark options={solid, mycolor5}]
  table[row sep=crcr]{%
1	0.00129716398391274\\
2	0.998702836015253\\
3	1.07370451326091e-15\\
4	8.33074594560992e-13\\
};
\addlegendentry{$\rho =1$}
